---
title: "ds202_hw3"
author: "Syed Hasan"
date: "2/18/2020"
output: html_document
---
```{r}
chooseCRANmirror(graphics = FALSE, ind=1)
knitr::opts_chunk$set(echo = TRUE)
```

```{r}
install.packages("lmtest")
install.packages('lmtest', repos = "http://cran.us.r-project.org")
install.packages('reshape2')
data(tips, package="reshape2")
```


```{r}
#Question 1
numParty <- nrow(tips)
numParty
```
Question 1

There were 244 Parties served



```{r}
#Question 2
str(tips)
```
Question 2

there are 7 columns, but with only three kind of variable num, Factor and int

Question 3
```{r}
#Question 3
day <- tips
day <- day[order(day$day),]
day
```
```{r}
#Question 4
female5 <- subset(tips, sex=="Female" & size >= 5,)
female5
```

Question 5
```{r}
install.packages("ggplot2")
library("ggplot2")
ggplot(data=tips, aes(x=total_bill, y=tip))+geom_jitter()
```

clearly the tip increases as the tota_bill increases

Question 6

Not a lot of people tip more than $4-$5 range. With only some outliers at $9-$10 tips

Question 7
```{r}
tiprate<-((mean(tips$tip)/mean(tips$total_bill))*100)
tiprate
```
The average tip rate is 15.15358

Question 8
```{r}
dinnerTip<- subset(tips, time == "Dinner" & tip)
lunchTip<- subset(tips, time == "Lunch" & tip)
mean(lunchTip$tip)
mean(dinnerTip$tip)
```
People spend more on tips during dinner time when compared to lunch time

Question 9

NOT DONE

Question 10
```{r}
ggplot(data=tips, aes(x=day, fill=sex))+geom_bar()
```
more females are eating outside on SAT, SUN and THUR.

